\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\usepackage[top=.35in, bottom=.35in, left=.5in, right=.5in]{geometry}

% \addtolength{\oddsidemargin}{-0.5in}
% \addtolength{\evensidemargin}{-0.5in}
% \addtolength{\textwidth}{1in}
% \addtolength{\topmargin}{-.5in}
% \addtolength{\bottom}{-.5in}
% \addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{\raisebox{0.35ex}{\tiny$\bullet$}}
\renewcommand{\labelitemi}{}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\hypersetup{colorlinks=true,urlcolor={blue}}


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\Large Andreas Santucci} &
\href{https://asantucci.github.io}{asantucci.github.io} \\
Email: \href{mailto:santucci.andreas@gmail.com}{santucci.andreas@gmail.com} &
Mobile: (650) 814 - 0024 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {Granica}{Mountain View, Calif.}
      {Research Scientist}{June 2025 - Present}
      \resumeItemListStart
        \resumeItem{\textbf{Predicting out of sample error in non-convex settings using Approximate Leave one Out} - \newline estimation of LOO Hessians via low rank updates of the full sample Hessian, masking eigen-directions associated with negative curvature in the LOO Hessian. Resulting prediction error for single index data generating processes with a mismatched Teacher-Student are within single digit percent error.}
        \resumeItem{\textbf{Large Tabular Models} - incorporating column semantics and measuring dataset generalization via per-example permutation of columns.}
      \resumeItemListEnd
    \resumeSubheading
      {Google}{Mountain View, Calif.}
      {Research Software Engineer}{Apr. 2023 - June 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Bard (Large Language Models)} - core contributor on \href{https://arxiv.org/pdf/2312.11805v4}{Gemini 1.5}.}
        \resumeItem{\textbf{YouTube (Spatial Super Resolution)} - via Diffusion Transformers.}
      \resumeItemListEnd
    \resumeSubheading
      {Google}{Mountain View, Calif.}
      {Senior Data Scientist}{Nov. 2018 - Apr. 2023}
        \resumeItemListStart
          \resumeItem{\textbf{Designed recommendation algorithms for YouTube Shorts} - grew the product from zero to billions of users.}
          \resumeItem{\textbf{Lead for Technical Infrastructure} - scaled YouTube Data Science team needs as we grew from 50 to 100 IC's.}
        \resumeItemListEnd
    \resumeSubheading
      {Stanford University}{Stanford, Calif.}
      {Lecturer (2017 - 2023); Teaching Fellow (2016-2017);
        Teaching Assistant (2016)}{Jan. 2016 - Mar. 2023}
      \resumeItemListStart
        \resumeItem{\textbf{Earned "Annual Best Lecturer" award 3x} - award is determined by both students and departmental-faculty.}
        \resumeItem{\textbf{Prepared and delivered lectures 2x/week}
          for CME 211 and 212 (intro and advanced scientific
          computing in Python and C++),
          with classes of 80 graduate students in STEM
          fields; managed a staff of four teaching assistants.
        }
          % Added to the core C++ curriculum RAII, move-semantics, templates, variadic arguments.}
        \resumeItem{\textbf{Engineered an AutoGrader system} in
          Python to
          facilitate programmatic grading of students' computer
          programs by fetching submissions % perform integration tests, assign meaningful feedback,
          and generating an interpretable grade report.}
        \resumeItem{\textbf{Synthesized lecture notes} for \href{https://stanford.edu/~rezab/classes/cme323/S17/}{CME 323}, a
          course in parallel and distributed algorithms.} %, which are still in use today!}
      \resumeItemListEnd
    \resumeSubheading
      {Airbnb}{San Francisco, Calif.}
      {Data Scientist}{Sep. 2018 - Nov. 2018}
    \resumeSubheading
      {Cardinal Analytx}{Palo Alto, Calif.}
      {Data Scientist}{Aug. 2017 - Aug. 2018}
      \resumeItemListStart
        \resumeItem{\textbf{Modeled health insurance claims data}
          using more than 80k features to predict a variety of
          outcomes, including nominal responses and
          orthopedic-joint surgeries. Built out the company's core product(s).}
          % \textbf{Enabled estimation of any response using
          %   claims data}, i.e. given a definition for a labeling
          % function,
          % our pipeline estimates the accuracy to which an insurer can predict
          % the response of interest using their own claims data.}
        \resumeItem{\textbf{Authored robust and extensible
            production quality machine learning pipelines} enabling
          state of the art results in a daily production
          cycle, improving performance 50\% beyond a
          \href{http://bmjopen.bmj.com/content/7/1/e011580}
          {BMJ Open 2017 research paper}.} %Generic programming allow seamless use across insurers in healthcare.}
        \resumeItem{\textbf{Lowered the memory footprint and compute
            time} by an order
          of magnitude.} % via sparse matrices; e.g. 80k features, 1/4M
                        % patients, 1/2-dozen time periods - takes $<
                        % 1$ hour and 24 GB RAM in R.}
        % \resumeItem{\textbf{Engineered 80k features} and realized a
        %   50\% improvement in core
        %   model performance over the original
        %   \href{http://bmjopen.bmj.com/content/7/1/e011580}
        %   {BMJ Open research paper} published in 2017.}
        \resumeItem{\textbf{Realized business value} by authoring both
          a risk-based model for actuarial purposes,
          outperforming state of the art compared with
          \href{https://www.soa.org/research-reports/2016/2016-accuracy-claims-based-risk-scoring-models/}{SOA's
            annual report},
          and also predicting orthopedic-joint surgeries in effort to route
          individuals from remote areas in Alaska and Washington to established
          centers of excellence.}
      \resumeItemListEnd
    \resumeSubheading
    {Lawrence Livermore National Lab}{Livermore, Calif.}
    {Computational Engineering Intern}{Summer 2015}
    \resumeItemListStart
      \resumeItem{\textbf{Contributed} to \texttt{SparkPlug}, a
        statistical project for Spark, written in
        Scala. Implemented distributed MCMC, Bayesian updating methods
        for use with conjugate priors, and relevant methods for
        extracting sufficient statistics.}
    \resumeItemListEnd
    \resumeSubheading
    {The Brattle Group}{San Francisco, Calif.}
    {Research Analyst}{May 2012 - June 2014}
    \resumeItemListStart
      \resumeItem{\textbf{Wrote a spell-checker using regular expressions} to recover
  thousands of GPS coordinates from a text-field on a proprietary
  survey with an accuracy rate of 97\%.}
      \resumeItem{\textbf{Used ArcGIS and Python} to combine various
        data sources and examine spatial patterns along the U.S. coastline.}
  % \textbf{Utilized ArcGIS, Python}, and disparate types of mapping data to
  % estimate, from scratch, the miles of coastline within each US state
  % (output was in consensus with NOAA estimates). Documented for use in
  % expert testimony.}
      \resumeItem{\textbf{Created and presented} eight R training sessions including parallel programming, web-scraping, and text mining.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Stanford University}{Stanford, Calif.}
      {M.S., computational mathematics, 3.96}{Aug. 2014 -- June 2017}
      \resumeItemListStart
        \resumeItem{Capstone thesis with Guido Imbens: estimated
          causal effects of night life on subsequent day sporting performance.}
        \resumeItem{Passed ICME Ph.D. qualifying exams in both
          stochastic processes as well as discrete mathematics and algorithms.}
    \resumeItemListEnd
    \resumeSubheading
      {University of California, Berkeley}{Berkeley, Calif.}
      {B.A., economics, 3.96}{Aug. 2010 -- May 2012}
      \resumeItemListStart
        \resumeItem{Highest Honors; thesis estimated causal effects
          of NCAA D1 sports participation on academic success.}
        \resumeItem{Student Athlete: ``walk-on'' for
          the swim
          and dive team, earned one of two spots on the diving travel
          squad. NCAA team championships in 2011 and
          2012.}
        \resumeItem{Neufeld Scholar: highest cumulative GPA among all
          student-athletes in 2012.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
